---
title: "612303050 Deshmukh Mehmood Rehan's Assignment 1"
output:
  html_document: default
---

Q1.Install packages namely ’plyr’, ’MASS’, ’ggplot2’, ’dplyr’ etc.
```{r}
#we can use vector to install multiple packages simultaneously
install.packages(c('plyr', 'MASS', 'ggplot2', 'dplyr'), repos = "http://cran.us.r-project.org")
```
Q2.Find answers to log2(2∧5) and log(exp(1)*exp(1))

```{r}
answer1 <- log2(2^5)
answer1
answer2 <- log(exp(1)*exp(1))
answer2
```

Q3.Using built-in dataset iris, implement the functions like: Summary, class, type of, 
head,tail, str, Merge.

```{r}
#loading dataset
data(iris)

#summary
iris_summary <- summary(iris)
iris_summary

#class
iris_class <- class(iris)
iris_class

#typeof
iris_typeof <- typeof(iris)
iris_typeof

#head
iris_head <- head(iris)
iris_head

#tail
iris_tail <- tail(iris)
iris_tail

#str
iris_str <- str(iris)

#merge
iris_merge <- merge(iris, iris, by = "Petal.Length")
head(iris_merge)
```

Q4.Write a R program to create a two-dimensional 5×3 array of sequence of even integers 
greater than 

```{r}
answer4 <- array(seq(from = 52, by = 2, length.out = 5*3), dim = c(5, 3))
answer4
```


Q5. Write a R program to create a vector which contains 10 integer values between -50 and 
+50

```{r}
answer5 <- seq(-50,50, 10)
answer5
```

Q6.Suppose the age is a vector containing ages of 10 persons as 
22,27,31,41,30,25,19,20,23,35

```{r}
age <- c(22, 27, 31, 41, 30, 25, 19, 20, 23, 35)

#a).Access the age of fourth person
answer6a <- age[4]
answer6a

#b).Create a vector of 'age 30' with a person >30
answer6b <- age[age > 30]
answer6b

#c).Access the age of last 3 person
answer6c <- tail(age, 3)
answer6c

#d).Find the number of elements in vector age
answer6d <- length(age)
answer6d
#e).Access the age of person except 5th and 7th
answer6e <- age[-c(5, 7)]
answer6e
#f).Create a vector 'age 2' with a persons between 20 and 25.
answer6f <- age[(age >= 20) & (age <= 25)]
answer6f
```

Q7.Create a factor from the following vector data:(1,2,3,2,3,1,4,2,3,NA,5,3,2) and also find 
levels

```{r}
answer7_factors <- factor(c(1, 2, 3, 2, 3, 1, 4, 2, 3, NA, 5, 3, 2))
answer7 <- levels(answer7_factors)
answer7
```

Q8.Write a R program to create a list containing strings, numbers, vectors and a logical 
values.

```{r}
answer8 <- list("abcd", 123, c(1, 2, 3), TRUE)
answer8
```


Q9.Using built-in dataset iris, find out the categorical variables.
```{r}
answer9 <- sapply(iris, is.factor)
answer9
```
Q10.Create a numeric vector c(1:5) and a 5 by 3 matrix with elements from 1 to 15.
```{r}
answer10_vector <- c(1:5)
answer10_matrix <- matrix(1:15, nrow = 5, ncol = 3)
answer10_vector
answer10_matrix
```

Q11. Create a dataframe of the following dataset
height:140,137,150,147,139,140,150,132,138,140
Weight:55,57,59,62,61,60,60,58,59,57
```{r}
answer11_dataframe <- data.frame(
  height = c(140, 137, 150, 147, 139, 140, 150, 132, 138, 140),
  weight = c(55, 57, 59, 62, 61, 60, 60, 58, 59, 57)
)

#a).Create a vector h1 with height>145cms
h1 <- answer11_dataframe$height[answer11_dataframe$height > 145]
h1
#b).Create a vector h2 with weight>55kgs
h2 <- answer11_dataframe$weight[answer11_dataframe$weight > 55]
h2
#c).Create a vector h3 with height>140 and weight >60
h3 <- answer11_dataframe$height[answer11_dataframe$height > 140 & answer11_dataframe$weight > 60]
h3
```